---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cellpanelr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

A Shiny app and R package for analyzing response data collected from panels of cell lines. It uses data sets and annotations publicly available from [DepMap](<https://depmap.org/portal/>) to identify features that correlate with user-provided data. These data sets are used under the [CC BY 4.0](<https://creativecommons.org/licenses/by/4.0/>) license.

## Shiny app

The shiny app is available at <https://dwassarman.shinyapps.io/cellpanelr/>

## Installation

You can install the development version of cellpanelr like so:

``` r
# install.packages("remotes")
remotes::install_github("dwassarman/cellpanelr")
```

To open and use the app locally:

```{r example, eval=FALSE}
library(cellpanelr)
run_app()
```


Please note that the cellpanelr project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
